Supporting information: Copulas and their potential for ecology

### 2019-12-17 SupportingInformation.Rmd
upto S20 BnW fig version added

<!--generating plots with sampling locations for soilCN data-->
```{r plot_SoilCNmapUSA, echo=F, results='hide'}
#---------map of soilCN location on USA------------
library(maps)
pdf("./Results/SoilCNmapUSA.pdf",height=4,width=8)
map("usa")
points(x = d$long, y = d$lat, col="red",pch=16,cex=0.5)
dev.off()
```

@@

pdf("./Results/aphid_map_plot.pdf")
map("world", fill=TRUE, col="grey84", bg="white",border=0, xlim=xlim, ylim=ylim)
map.axes(cex.axis=2.5)
points(x = df_loc_info_org$longs, y = df_loc_info_org$lats, col="red",pch=16)
points(x = df_loc_info$longs, y = df_loc_info$lats, col="blue", pch=0, cex=1.5)
text(df_loc_info_org$loc_no, x = df_loc_info_org$longs, y = df_loc_info_org$lats, col="red",  pos=1)
dev.off()

@@

pdf("./Results/plankton_map_plot.pdf")
map("world", fill=TRUE, col="grey84", bg="white",border=0, xlim=xlim, ylim=ylim)
map.axes(cex.axis=2.5)
abline(h=seq(from=ylim[1],to=ylim[2],by=2), v=seq(from=xlim[1],to=xlim[2],by=2), col="black", lty=2)
points(x = df_loc_info_org$longs+1, y = df_loc_info_org$lats+1, col="red",pch=16)
points(x = df_loc_info$longs+1, y = df_loc_info$lats+1, col="blue", pch=0, cex=1.5)
text(df_loc_info_org$loc_no, x = df_loc_info_org$longs+1, y = df_loc_info_org$lats+1, col="red",  pos=1)
dev.off()
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=16 cm]{./Results/aphid_map_plot.pdf} 
\caption[Sampling locations for aphid data]{Locations of the 
Rothamsted Insect Survey 
suction traps from which data were available are indicated by the red circles, 
out of which only blue boxes had at least 30 years of data and were 
used for our study. \label{fig_aphid_map}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=16 cm]{./Results/plankton_map_plot.pdf} 
\caption[Sampling regions for CPR plankton data]{CPR data were available from 
26 locations ($2^{\circ}$ $\times$ $2^{\circ}$ regions on the map) around UK 
seas (red circles), out of which only blue boxes had at least 45 years of data and
were used for our study. \label{fig_plankton_map}}
\end{center}
\end{figure}

@@

<!--Simulation for testing non-parametric statistics with different copulas :
The message=F is to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a message.-->
```{r stat_testing_save_and_plot_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,busycores,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

@@

b<-callfn$paramlist
plotter_stat_testing(res_pt35_rankF,"res_pt35_rankF",b,resultsloc,spearvals)
plotter_stat_testing(res_pt35_rankT,"res_pt35_rankT",b,resultsloc,spearvals)
plotter_stat_testing(res_pt1000_rankF,"res_pt1000_rankF",b,resultsloc,spearvals)
plotter_stat_testing(res_pt1000_rankT,"res_pt1000_rankT",b,resultsloc,spearvals)
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt35_rankT.pdf}
\caption[Testing nonparametric statistics with 35 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence of the normal and Frank copulas. See Appendix  \ref{Test_npa_stat} for details. $n=35$. \label{fig_stat_testing35}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt1000_rankT.pdf}
\caption[Testing nonparametric statistics with 1000 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence of the normal and Frank copulas. See Appendix  \ref{Test_npa_stat} for details. $n=1000$.\label{fig_stat_testing1000}}
\end{center}
\end{figure}

>>>>

<!--generating plots with sampling locations for soilCN data-->
```{r plot_SoilCNmapUSA, echo=F, results='hide'}
#---------map of soilCN location on USA------------
library(maps)
pdf("./Results/SoilCNmapUSA.pdf",height=4,width=8)
map("usa")
points(x = d$long, y = d$lat, col=rgb(0,0,0,0.2),pch=16,cex=0.5)
dev.off()
```

@@

pdf("./Results/aphid_map_plot.pdf")
map("world", fill=TRUE, col="grey84", bg="white",border=0, xlim=xlim, ylim=ylim)
map.axes(cex.axis=2.5)
points(x = df_loc_info_org$longs, y = df_loc_info_org$lats, col="black",pch=16)
points(x = df_loc_info$longs, y = df_loc_info$lats, col="black", pch=0, cex=1.5)
text(df_loc_info_org$loc_no, x = df_loc_info_org$longs, y = df_loc_info_org$lats, col="black",  pos=1)
dev.off()

@@

pdf("./Results/plankton_map_plot.pdf")
map("world", fill=TRUE, col="grey84", bg="white",border=0, xlim=xlim, ylim=ylim)
map.axes(cex.axis=2.5)
abline(h=seq(from=ylim[1],to=ylim[2],by=2), v=seq(from=xlim[1],to=xlim[2],by=2), col="black", lty=2)
points(x = df_loc_info_org$longs+1, y = df_loc_info_org$lats+1, col="black",pch=16)
points(x = df_loc_info$longs+1, y = df_loc_info$lats+1, col="black", pch=0, cex=1.5)
text(df_loc_info_org$loc_no, x = df_loc_info_org$longs+1, y = df_loc_info_org$lats+1, col="black",  pos=1)
dev.off()
```

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=16 cm]{./Results/aphid_map_plot.pdf} 
\caption[Sampling locations for aphid data]{Locations of the 
Rothamsted Insect Survey 
suction traps from which data were available are indicated by the circles, 
out of which only squares had at least 30 years of data and were 
used for our study. \label{fig_aphid_map}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=16 cm]{./Results/plankton_map_plot.pdf} 
\caption[Sampling regions for CPR plankton data]{CPR data were available from 
26 locations ($2^{\circ}$ $\times$ $2^{\circ}$ regions on the map) around UK 
seas (circles), out of which only squares had at least 45 years of data and
were used for our study. \label{fig_plankton_map}}
\end{center}
\end{figure}

@@

<!--Simulation for testing non-parametric statistics with different copulas :
The message=F is to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a message.-->
```{r stat_testing_save_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,busycores,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

@@

b<-callfn$paramlist

plotter_stat_testing(reslist=res_pt35_rankF,filename="res_pt35_rankF",xaxparams=b,resultsloc,spearvals)
plotter_stat_testing(reslist=res_pt35_rankT,filename="res_pt35_rankT",xaxparams=b,resultsloc,spearvals)
plotter_stat_testing(reslist=res_pt1000_rankF,filename="res_pt1000_rankF",xaxparams=b,resultsloc,spearvals)
plotter_stat_testing(reslist=res_pt1000_rankT,filename="res_pt1000_rankT",xaxparams=b,resultsloc,spearvals)
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt35_rankT.pdf}
\caption[Testing nonparametric statistics with 35 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence of the normal and Frank copulas. p-values (indicated by the triangles) when less than $0.05$ (below the dashed line) mean there is significant tail asymmetry. See Appendix  \ref{Test_npa_stat} for details. $n=35$. \label{fig_stat_testing35}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt1000_rankT.pdf}
\caption[Testing nonparametric statistics with 1000 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence of the normal and Frank copulas. p-values (indicated by the triangles) when less than $0.05$ (below the dashed line) mean there is significant tail asymmetry. See Appendix  \ref{Test_npa_stat} for details. $n=1000$.\label{fig_stat_testing1000}}
\end{center}
\end{figure}
